---
title: "TEAM 2 - I want to be a Billionaire"
output:
  html_document:
    df_print: paged
---

# DATA LOADING, DATA STRUCTURE

```{r message=FALSE}
'install.packages("tidyverse")
install.packages("countrycode")
install.packages("moderndive")'
library(dplyr)
library(ggplot2)
library(countrycode)
library(moderndive)

baires <- read.csv("Forbes Billionaires.csv")
baires$continent <- countrycode(sourcevar = baires[, "Country"],
                            origin = "country.name",
                            destination = "continent")

str(baires)
```

# INTRODUCTION AND QUICK FACTS

## NETWORK RANGE OF BILLIONAIRES - MAX, MIN, MEAN

```{r}
nw_descriptive_stats <- c(nrow(baires), max(baires$Networth), min(baires$Networth), mean(baires$Networth), median(baires$Networth))
names(nw_descriptive_stats) <- c("Number of billionaires", "Highest net worth", "Lowest net worth", "Average net worth", "Median net worth")
nw_descriptive_stats
```

## RICHEST, YOUNGEST, OLDEST, MALAYSIAN BILLIONAIRES

```{r}
richest_baires <- baires %>%
    arrange(desc(Networth)) %>%
    head(n = 10L)

youngest_baires <- baires %>%
    arrange(Age) %>%
    head(n = 10L)

oldest_baires <- baires %>%
    arrange(desc(Age)) %>%
    head(n = 10L)

MY_baires <- baires %>%
    filter(Country == "Malaysia") %>%
    arrange(desc(Networth))
  

richest_baires
youngest_baires
oldest_baires
MY_baires
```

## AGE RANGE OF BILLIONAIRES - OLDEST, YOUNGEST, AVERAGE AGE

```{r}
age_descriptive_stats <- c(max(baires$Age), min(baires$Age), mean(baires$Age), median(baires$Age))
names(age_descriptive_stats) <- c("Oldest", "Youngest", "Average age", "Median age")
age_descriptive_stats
```

## THE TEN OLDEST AND YOUNGEST BILLIONAIRES IN THE WORLD

```{r}
oldest_baires <- baires %>%
    arrange(desc(Age)) %>%
    head(n = 10L)

youngest_baires <- baires %>%
    arrange(Age) %>%
    head(n = 10L)

oldest_baires
youngest_baires 

```

## SOURCE OF WEALTH

```{r}
baires %>%
  group_by(Source) %>%
  summarize(sum_nw = sum(Networth)) %>%
  arrange(desc(sum_nw))

```

# BUBBLE CHART ANALYSIS

## Net Worth X Number X Industry

```{r}
by_indstry <- baires %>%
  group_by(Industry) %>%
  summarize(sum_nw = sum(Networth), avg_nw = mean(Networth), n = n()) %>%
  arrange(sum_nw)

ggplot(by_indstry, aes(sum_nw, n, size = avg_nw, color = Industry)) +
  geom_jitter() +
  labs(title = "Billionaires by industry, net worth, and count",
       x = "Number of billionaires",
       y = "Total net worth (log scale)"
  ) +
  scale_y_log10() +
  geom_text(aes(label=Industry, size = 4), vjust=-1)
```

## Net Worth X Number X Country X Continent

```{r}
by_cntry <- baires %>%
  group_by(Country) %>%
  summarize(sum_nw = sum(Networth), avg_nw = mean(Networth), n = n(), continent = unique(continent)) %>%
  arrange(sum_nw)

ggplot(by_cntry, aes(sum_nw, avg_nw, size = n, color = continent)) +
  geom_point() +
  labs(title = "Average vs Total net worth by country and number of billionaires",
       x = "Total net worth (log scale)",
       y = "Average net worth"
       ) +
  scale_x_log10() +
  geom_text(aes(label=Country, size = 100, vjust=-1.25))
```

## Rank X Age X Net Worth X Industry

```{r}
baires %>%
  filter(Rank <= 200) %>%
    ggplot(aes(Rank, Age, size = Networth, color = continent )) +
    geom_jitter() +
    labs(title = "Top 200 billionaires by rank, age, net worth, and continent",
       x = "Rank",
       )
 
```

## Rank X Age X Net Worth X Industry X Continent

```{r}
baires %>%
  filter(Rank <= 200) %>%
    ggplot(aes(Rank, Age, size = Networth, color = Industry )) +
    geom_jitter() +
    facet_wrap(~continent) +
    labs(title = "Top 200 billionaires by rank, age, net worth, and industry",
       x = "Rank",
       )
 
```

# COUNTRY ANALYSIS

## Column: Number of billionaires by country

```{r}
num_by_cntry <- baires %>%
  group_by(Country) %>%
  summarize(n = n()) %>%
  arrange(desc(n))

total_baires <- nrow(baires)

per_by_cntry <- num_by_cntry %>%
  mutate(percentage = num_by_cntry$n/total_baires*100)

top10_per_by_cntry <- head(per_by_cntry, n = 10)

ggplot(top10_per_by_cntry, aes(reorder(Country, -n), n, fill = Country)) +
  geom_col() +
  theme(legend.position = "none",
        axis.title.x=element_blank()) +
  labs(title = "Number of billionaires by country",
       subtitle = "US and China has the largest number of billionaires globally",
       y = "Number of billionaires"
       ) +
  geom_text(aes(label=round(n,1)), vjust=-0.25)

```

## Net Worth by Country x Industry

```{r}
top10c <- top10_per_by_cntry$Country

nw_by_cntry_x_indstry <- baires %>%
  filter(Country == top10c) %>%
  group_by(Country, Industry) %>%
  summarize(sum_nw = sum(Networth))

ggplot(nw_by_cntry_x_indstry, aes(Country, sum_nw, fill = Industry)) +
  geom_col() +
  theme(axis.title.x=element_blank()) +
  labs(title = "Net worth by country and industry",
       y = "$ billion"
       ) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.75)) 

```

## Histogram: Number of billionaires by country

```{r}

ggplot(num_by_cntry, aes(n)) +
  geom_histogram() +
  theme(legend.position = "none") +
  labs(title = "Histogram of number of billionaires by country",
       subtitle = "Most countries in this list only have 1 billionaire",
       x = "Number of billionaires"
       ) +
  scale_x_log10()

```

## Column: Net worth by country

```{r}
nw_by_cntry <- baires %>%
  group_by(Country) %>%
  summarize(sum_nw = sum(Networth)) %>%
  arrange(desc(sum_nw))

total_nw <- sum(baires$Networth)

pernw_by_cntry <- nw_by_cntry %>%
  mutate(percentage = nw_by_cntry$sum_nw/total_nw*100)

top10_pernw_by_cntry <- head(pernw_by_cntry, n = 10)

ggplot(top10_pernw_by_cntry, aes(reorder(Country, -sum_nw), sum_nw, fill = Country)) +
  geom_col() +
  theme(legend.position = "none",
        axis.title.x=element_blank()) +
  labs(title = "Total net worth of billionaires by country",
       subtitle = "Net worth of US billionaires are substantially larger than the rest",
       y = "$ billion"
       ) +
  geom_text(aes(label=round(sum_nw,1)), vjust=-0.25)

```

## Histogram: Net worth of billionaires by country

```{r}

ggplot(nw_by_cntry, aes(sum_nw)) +
  geom_histogram() +
  theme(legend.position = "none") +
  labs(title = "Histogram of net worth of billionaires by country",
       x = "$ billion"
       ) +
  scale_x_log10()

```

# INDUSTRY ANALYSIS

## Column: Number of billionaires by industry

```{r}
no_by_indstry <- baires %>%
  group_by(Industry) %>%
  summarize(n = n()) %>%
  arrange(desc(n))

perno_by_indstry <- no_by_indstry %>%
  mutate(percentage = no_by_indstry$n/total_baires*100)

top10_perno_by_indstry <- head(perno_by_indstry, n = 10)

ggplot(top10_perno_by_indstry, aes(reorder(Industry, -n), n, fill = Industry)) +
  geom_col() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, vjust=0.75)) +
  labs(title = "Share of billionaires' net worth by industry",
       x = "Industry",
       y = "Number of billionaires"
       ) +
  geom_text(aes(label=round(n,1)), vjust=-0.15)

```

## Column: Net worth by industry

```{r}
nw_by_indstry <- baires %>%
  group_by(Industry) %>%
  summarize(sum_nw = sum(Networth)) %>%
  arrange(desc(sum_nw))

total_nw <- sum(baires$Networth)

pernw_by_indstry <- nw_by_indstry %>%
  mutate(percentage = nw_by_indstry$sum_nw/total_nw*100)

top10_pernw_by_indstry <- head(pernw_by_indstry, n = 10)

ggplot(top10_pernw_by_indstry, aes(reorder(Industry, -sum_nw), sum_nw, fill = Industry)) +
  geom_col() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, vjust=0.75),
        axis.title.x=element_blank()) +
  labs(title = "Share of billionaires' net worth by industry",
       y = "$ billion"
       ) +
  geom_text(aes(label=round(sum_nw,1)), vjust=-0.5)

```

## Column: Number of billionaires by industry and continent

```{r}
num_by_indstry_x_continent <- baires %>%
  group_by(Industry, continent) %>%
  summarize(n = n())

ggplot(num_by_indstry_x_continent, aes(Industry, n, fill = continent)) +
  geom_col() +
  theme(axis.title.x=element_blank()) +
  labs(title = "Number of billionaires by industry and continent",
       y = "Count"
       ) +
  theme(axis.text.x = element_text(angle = 90, vjust=0.5)) 

```

## Column: Net worth by industry and continent

```{r}
nw_by_indstry_x_continent <- baires %>%
  group_by(Industry, continent) %>%
  summarize(sum_nw = sum(Networth))

ggplot(nw_by_indstry_x_continent, aes(Industry, sum_nw, fill = continent)) +
  geom_col() +
  theme(axis.title.x=element_blank()) +
  labs(title = "Net worth of billionaires by industry and continent",
       y = "$ billion"
       ) +
  theme(axis.text.x = element_text(angle = 90, vjust=0.5)) 

```

# AGE ANALYSIS

## Histogram

```{r}

ggplot(baires, aes(Networth)) +
  geom_histogram() +
  theme(legend.position = "none") +
  labs(title = "Histogram of net worth of billionaires by country",
       subtitle = "Most billionaies have around $1 - $2 billion",
       x = "Number of billionaires (log scale)",
       y = "count (log scale)"
       ) +
  scale_x_log10() +
  scale_y_log10()

ggplot(baires, aes(Age)) + 
  geom_histogram(binwidth = 10) +
  labs(title = "Histogram of age of billionaires by country",
       subtitle = "Median age of 64 years old",
       x = "Age"
       )

```

## Age by Continent

```{r}
ggplot(baires, aes(Age, fill = continent)) +
  geom_histogram(binwidth = 10) +
  facet_grid(~continent) +
  theme(legend.position = "none") +
  scale_y_log10() +
  labs(title = "Histogram of billionaires' age by continent",
       x = "Age",
       y = "Count (log scale)"
       )

ggplot(baires, aes(continent, Age)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  scale_y_log10() +
  labs(title = "Boxplot of billionaires' age by continent",
       subtitle = "Median age of billionaires in Asia younger than others",
       y = "Age"
       )

```

##Age by Industry

```{r}

top10i <- top10_pernw_by_indstry$Industry

baires %>%
  filter(Industry == top10i) %>%
  ggplot(aes(Industry, Age)) +
  geom_boxplot() +
  labs(title = "Boxplot of billionaire by industry and age",
       x = "Industry",
       y = "Age"
       ) +  
  theme(axis.text.x = element_text(angle = 10, vjust=0.75),
        axis.title.x = element_blank()) 
  
```

# REGRESSION

## Regression

```{r}

baires$continent <- factor(baires$continent, ordered = FALSE)

baires$continent <- relevel(baires$continent, ref = "Asia")

model <- lm(log10(Networth) ~ Age + continent, data = baires)
get_regression_table(model)
 
```

## Regression - Coefficients

```{r}

regtab <- get_regression_table(model)

regtab %>%
  filter(p_value <=0.1) %>%
  ggplot(aes(term, 10^(estimate), fill = term)) +
    geom_col() +
    labs(title = "Coefficients of variables with p_value <= 0.05",
       x = "Variable",
       y = "Coefficient ($ billion)"
       ) +
    geom_text(aes(label=round(10^estimate,4), vjust=-.5))
 
```
